\documentclass[letterpaper,12pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[bookmarks=true,pdfborder={0 0 0}]{hyperref}
\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright

\author{Marwan Osman}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}
\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}   #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-8pt} \hrulefill \\}
\newcommand{\interval}[1] { \textit{(#1)} }
\newcommand{\header}[1]{{\hspace*{0pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} - {#3} \interval{#2}\\ }}
\newcommand{\education}[3]{{\textbf{#1} \interval{#2}\\{#3}\\ }}
\newcommand{\projects}[2]{{ \textbf{#1} #2\\ }}
\newcommand{\objective}[1]{{#1\\\vspace*{8pt}}}
\newcommand{\contact}[3]{
\vspace*{-8pt}
%\begin{center}
{\LARGE \scshape {#1}}\\
#2 \lineunder 
#3
%\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}
\newenvironment{details}{\vspace*{-4pt} \begin{list}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}
% END RESUME DEFINITIONS

\begin{document}
\small
\smallskip
\vspace*{-30pt}

\contact{Marwan Osman}
{\textbf{Address:} 21 Ahmed Kamha St., Camp Caesar, Alexandria, Egypt \textbf{Mobile:} +201222403046
\\\textbf{Email:} \href{mailto:marwan.aosman@gmail.com}{marwan.aosman@gmail.com} \textbf{Website:} \url{http://www.marwanosman.com}
}

\vspace*{16pt}

% PROFESSIONAL OBJECTIVE %
\header{Professional Objective}
\objective{ To make a contribution in progressing computers intelligence through creating and building smart intelligent web and mobile applications.
Searching and looking to bring the latest state of the art from academia, to design and build smarter intelligent and useful products.}

% EDUCATION %
\header{Education}
\education{B. Sc. Computer and Systems Engineering}{2005 - 2010}{Faculty of Engineering, Alexandria University, Egypt. Cumulative GPA: 3.18}
  \begin{details}
    \item \textbf{ Graudation Project "WNMI":} Web Networks and Mail Integrator
    \item \textbf{ Abstract:} A web framework integrating various social networks and mail providers, providing extensibility to any new coming network. WNMI is implemented in a web interface and a desktop interface featuring offline synchronization. The main concept of the project is to adhere with the rapid pace of emerging soical networks and combine all the user's social streams in on user-friendly interface.
    \item \textbf{ Technologies used:} J2EE, JavaFX and client libraries for different social networks and mail providers.
  \end{details}
\vspace*{4pt}
\education{General Secondary Certificate(G.S.C.)(Mathematics Division)}{2003 - 2005}{Saint Marc College, Alexandria, Egypt. Cumulative Score: 97\%}
\vspace*{4pt}

% WORK EXPERIANCE %
\header{Experiance}
\employer{eSpace Technologies}{July 2010 - Present}{Junior Web Developer}
  \begin{achievements}
    \item Developing cutting edge social applications with the Ruby on Rails stack.
    \item Project \textit{Marginize}, \url{http://www.marginize.com} \interval{August 2010 - May 2011}
    \begin{details}
      \item A social tool that adds a margin to any public webpage, enabling users to interact on top of it, checking in, adding comments and reading discussions about it pulled from social networks. 
    \end{details}
    \item Project \textit{Nextly}, \url{http://nextly.com} \interval{May 2001 - Present}
    \begin{details}
      \item A social streams browser that enhances the user experience browsing twitter, facebook and rss feeds, in a more modern way that is fast, efficient and user-friendly. 
    \end{details}
    \item Due to the nature of these 2 projects being developed for a startup company, my responsibilities were varying from fast prototyping on new features, front-end and back-end support for the features, adding analytics and measure data about users behaviours, and some system administration tasks.
    \item Partcipating in company's hack days, implementing ideas such as: 'The Industrial-Strength Audio Search Algorithm' empowering Shazam, an Android Time tracker app, a javascript tool to easily create guided tours for web applications.
    \item Presenting Technical sessions for colleagues: 'Edge Rank Algorithm' used to populate the Facebook news feed feature, and 'Bloom Filters' and how they can be used to implement a trending topics algorithms like on Twitter.
  \end{achievements}
\vspace*{4pt}
\employer{ITWorx}{July - August, 2009}{Software Quality Engineer - Intern}
  \begin{achievements}
    \item Worked on software testing automation on one of ITWorx products called I-Sales, using IBM Rational Functional Tester and writing test scripts in Java.
    \item Presented an introduction session to the basics of Java language to some of my team members.
    \item Contributed in defining a framework for future automation projects based on an object oriented framework for IBM RFT proposed by IBM.
  \end{achievements}
\vspace*{4pt}

\newpage

% TECHNICAL SKILLS %
\header{Technical Skills}
\begin{achievements}
  \item \textbf{Good Experience with:} Object Oriented Programming, Design Patterns, Agile Programming.
  \item \textbf{Programming Languages:} Java, C/C++, Basic, 8086 Assembly, Python, Ruby.
  \item \textbf{Web Development:} HTML, CSS, JavaScript, XML, AJAX, JSON, JavaFX.
  \item \textbf{DBMS:} Microsoft Access, MySQL, SQLite, Oracle 10g.
  \item \textbf{Platforms:} Windows 95/98/2000/XP/Vista/7, GNU/Linux Ubuntu.
  \item \textbf{Mobile Platforms:} Symbian, J2ME, Android.
  \item \textbf{IDEs:} Eclipse, Microsoft Visual Studio.NET, NetBeans.
  \item \textbf{Digital Design:} VHDL, Xilinx, ModelSim.
  \item \textbf{Design and Graphics Software (Fair knowledge):} Adobe Photoshop, 3D Studio Max, Adobe Premiere, Adobe Macromedia Flash.
\end{achievements}
\vspace*{4pt}

% PERSONAL SKILLS %
\header{Personal Skills}
\begin{tabular}{l l l l}
$\bullet$ Team Working& 
$\bullet$ Time Management&
$\bullet$ Self Learner& 
$\bullet$ Working under pressure\\
\end{tabular}
\vspace*{4pt}

% LANGUAGES %
\header{Languages}
\begin{tabular}{l l l}
$\bullet$ \textbf{Arabic:} Native& 
$\bullet$ \textbf{English:} Fluent (TOEFL iBT 97,2012)&
$\bullet$ \textbf{French:} Fluent (DELF certified,2004)\\
\end{tabular}
\vspace*{4pt}

% ACTIVITIES %
\header{Extra Curricular Activities}
\begin{achievements}
  \item Enrolling in Coursera and Udacity online courses: AI, Machine Learning, Programming a Robotic Car, Computer Vision Fundamentals, Heterogenous Parallel Programming.
  \item Implemented a Vim plugin to reload your browser automatically on file save using xdotools on Gnome Linux. \interval{March, 2012} \href{https://github.com/lordm/vim-browser-reload-linux}{Github repo}
  \item Presented a 101 session for Information Technology Institute (ITI) about \textbf{Python and Google App Engine} \interval{May, 2011}
  \item Participated in \textbf{Startup Weekend Cairo 2011}, Project \textbf{Jayyim} \interval{April, 2011}
    \subitem A real-time guitar amp and effects modeling mobile application for Android.
  \item Participated in organization of \textbf{Software Freedom Day@Alexandria University} festival \interval{September, 2009}
    \subitem Supervised a study group about Python.
    \subitem Presented a session about "Programming under Linux in Python".
  \item Participated in \textbf{Microsoft Imagine Cup booth in the Faculty of Engineering, Alexandria University} \interval{November, 2008}
  \item Attended \textbf{IEEE-ASST 3rd annual event "Leading your career, Leading your society"}, and associated workshop "Effective Time Management" \interval{September, 2007}
  \item Attended \textbf{Algorithms and programming training for EOI} \interval{June - September, 2007}
    \subitem \textit{Topics:} Graphs structure and algorithms, Backtracking, Geometric Algorithms, Binary Search Trees, Heaps, Dynamic Programming.
\end{achievements}

\end{document}
